An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2014-04-01 mixedwindow.tex
Move assumptions from theorem to stand alone

\newtheorem{thm}{Theorem}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{claim}[thm]{Claim}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{lema}{Lemma}[section]
\newtheorem{alg}{Algorithm}
\newtheorem{asmp}{Assumption}[section]

@@

\begin{thm}\label{res:1}
  Suppose that we have two models $\hat{y}_{0t}$ and $\hat{y}_{1t}$ to
  forecast the variable $y_t$, and have observations for
  $t=1,\dots,T+1$.  Assume the following hold:
  \begin{enumerate}
  \item \label{item:1} The benchmark forecast $\hat{y}_{0,t+1}$, is
    estimated using \ols\ with a recursive window:
    $\hat{y}_{0,t+1} = x_t'\hat{\beta}_t$ for some vector of
    predictors $x_t$ with $\hat{\beta}_t$ given by
    Equation~\eqref{eq:8}.  Also define $\btrue = (\E x_{t-1}
    x_{t-1}')^{-1} \E x_{t-1} y_t$ and assume that $\btrue$ does not depend
    on~$t$.
  \item \label{item:2} The alternative forecast, $\hat{y}_{1t}$, is
    estimated using a rolling window of fixed length $R$ (which is
    less than $T$), so $\hat{y}_{1,t+1} =
    \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})$ where $\psi$ is a known
    function and $z_t$ is a sequence of predictors that may include
    $x_t$.
  \item \label{item:3} The series $y_t$, $\hat{y}_{1t}$, and $x_t$
    have uniformly bounded $2 r$ moments for some $r > 2$, and $\hat
    y_t y_t$ $\hat y_t x_{t-1}$, $y_t x_{t-1}$, and $x_{t-1},
    x_{t-1}'$ are $L_2$-\ned\ of size $-\frac12$ on a strong mixing
    series of size $-\frac{r}{r-2}$ for $r>2$ or a uniform mixing
    series of size $-\frac{r}{2r-2}$.
  \item \label{item:4} Define \[f_t(\beta) = (y_{t+1} - x_t'\beta)^2 -
    (y_{t+1} - \hat{y}_{1,t+1})^2 + (x_t'\beta - \hat{y}_{1,t+1})^2,\]
    $f_t = f_t(\beta_0)$, $\hat f_t = f_t(\hat\beta_t)$,
    $\bar{f}(\beta) = \oavg{t} f_t(\beta)$, and $\bar f
    = \tfrac1P \sum_{t=R+1}^{T} \hat f_t$, with $P = T - R$;
    $\bar f(\btrue)$ has uniformly positive and finite long run
    variance.
  \end{enumerate}
  Under the null hypothesis that $y_t - \hat{y}_{0t}(\btrue)$ is a
  martingale difference sequence with respect to the filtration
  $\mathcal{F}_t = \sigma((y_t, z_{t}), (y_{t-1}, z_{t-1}),\dots)$,
  $\tfrac{\sqrt{P}}{\hat\sigma} \bar f \to^d N(0,1)$, where 
  \begin{align*}
    \hat{\sigma}^2 &= \hat{S}_{ff} + 2 \Pi (\hat{S}_{fg} + \hat{S}_{gg}), &
    \hat{S}_{ff} &= \oavg{t} (\hat f_t - \bar f)^2, \\
    \hat{S}_{fg} &= \oavg{t} (\hat f_t - \bar{f})(\hat g_t - \bar g)', &
    \hat{S}_{gg} &= \oavg{t} (\hat g_t - \bar g)(\hat g_t - \bar g)',
  \end{align*}
  $\Pi = 1 - \tfrac{R}{P} \log(1 + \tfrac{P}{R})$, $\bar{g} = \oavg{t}
  \hat g_t$, $\X' = [x_1,\dots,x_T]$,
  \begin{equation*}
    g_t(\beta) =
    \Big\{\tfrac{2}{P}\sum_{s=R}^T x_s (x_s'\beta - \hat{y}_{1,s+1}) \Big\}'
    \big(\tfrac1T \X'\X \big)^{-1} x_t(y_{t+1} - x_t'\beta),
  \end{equation*}
  and $\hat g_t = g_t(\hat\beta_t)$.
\end{thm}

>>>>

\newtheorem{thm}{Theorem}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{claim}[thm]{Claim}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{lema}{Lemma}[section]
\newtheorem{alg}{Algorithm}
\newtheorem{asmp}{Assumption}

@@

\begin{asmp}\label{a1}%
  The benchmark forecast $\hat{y}_{0,t+1}$, is estimated using \ols\
  with a recursive window: $\hat{y}_{0,t+1} = x_t'\hat{\beta}_t$ for
  some vector of predictors $x_t$ with $\hat{\beta}_t$ given by
  Equation~\eqref{eq:8}.  Also define $\btrue = (\E x_{t-1}
  x_{t-1}')^{-1} \E x_{t-1} y_t$ and assume that $\btrue$ does not
  depend on~$t$.
\end{asmp}

\begin{asmp}\label{a2}%
  The alternative forecast, $\hat{y}_{1t}$, is estimated using a
  rolling window of fixed length $R$ (which is less than $T$), so
  $\hat{y}_{1,t+1} = \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})$ where
  $\psi$ is a known function and $z_t$ is a sequence of predictors
  that may include $x_t$.
\end{asmp}

\begin{asmp}\label{a3}%
  The series $y_t$, $\hat{y}_{1t}$, and $x_t$ have uniformly bounded
  $2 r$ moments for some $r > 2$, and $\hat y_t y_t$ $\hat y_t
  x_{t-1}$, $y_t x_{t-1}$, and $x_{t-1}, x_{t-1}'$ are $L_2$-\ned\ of
  size $-\frac12$ on a strong mixing series of size $-\frac{r}{r-2}$
  for $r>2$ or a uniform mixing series of size $-\frac{r}{2r-2}$.
\end{asmp}

\begin{asmp}\label{a4}%
  Define \[f_t(\beta) = (y_{t+1} - x_t'\beta)^2 - (y_{t+1} -
  \hat{y}_{1,t+1})^2 + (x_t'\beta - \hat{y}_{1,t+1})^2,\] $f_t =
  f_t(\beta_0)$, $\hat f_t = f_t(\hat\beta_t)$, $\bar{f}(\beta) =
  \oavg{t} f_t(\beta)$, and $\bar f = \tfrac1P \sum_{t=R+1}^{T} \hat
  f_t$, with $P = T - R$; $\bar f(\btrue)$ has uniformly positive and
  finite long run variance.
\end{asmp}

\begin{thm}\label{res:1}
  Suppose that we have two models $\hat{y}_{0t}$ and $\hat{y}_{1t}$ to
  forecast the variable $y_t$, and have observations for
  $t=1,\dots,T+1$. Suppose that Assumptions~\ref{a1} -- \ref{a4} hold.
  Under the null hypothesis that $y_t - \hat{y}_{0t}(\btrue)$ is a
  martingale difference sequence with respect to the filtration
  $\mathcal{F}_t = \sigma((y_t, z_{t}), (y_{t-1}, z_{t-1}),\dots)$,
  $\tfrac{\sqrt{P}}{\hat\sigma} \bar f \to^d N(0,1)$, where 
  \begin{align*}
    \hat{\sigma}^2 &= \hat{S}_{ff} + 2 \Pi (\hat{S}_{fg} + \hat{S}_{gg}), &
    \hat{S}_{ff} &= \oavg{t} (\hat f_t - \bar f)^2, \\
    \hat{S}_{fg} &= \oavg{t} (\hat f_t - \bar{f})(\hat g_t - \bar g)', &
    \hat{S}_{gg} &= \oavg{t} (\hat g_t - \bar g)(\hat g_t - \bar g)',
  \end{align*}
  $\Pi = 1 - \tfrac{R}{P} \log(1 + \tfrac{P}{R})$, $\bar{g} = \oavg{t}
  \hat g_t$, $\X' = [x_1,\dots,x_T]$,
  \begin{equation*}
    g_t(\beta) =
    \Big\{\tfrac{2}{P}\sum_{s=R}^T x_s (x_s'\beta - \hat{y}_{1,s+1}) \Big\}'
    \big(\tfrac1T \X'\X \big)^{-1} x_t(y_{t+1} - x_t'\beta),
  \end{equation*}
  and $\hat g_t = g_t(\hat\beta_t)$.
\end{thm}
